\documentclass[line, margin]{res}
\usepackage{bibentry}
 \usepackage{natbib} 
\usepackage{marvosym}
\usepackage{wasysym}
\usepackage{fontawesome5}
\usepackage{twemojis}
\usepackage[hidelinks]{hyperref}
\newcommand{\plus}{\nolinebreak\hspace{-.05em}\raisebox{.3ex}{\scriptsize\bf +}}
\newcommand{\Cpp}{C\nolinebreak\hspace{-.05em}\raisebox{.3ex}{\scriptsize\bf ++}}
\newcommand{\au}{\twemoji{flag: Australia}}
\newcommand{\uk}{\twemoji{flag: United Kingdom}}
\newcommand{\ita}{\twemoji{flag: Italy}}
\newcommand{\us}{\twemoji{flag: United States}}

\begin{document}
\bibliographystyle{unsrt}
\nobibliography{ref}

\name{{\LARGE \sc Alexander Mascolo}}
\address{\small\texttt{
\faGlobe \ \url{https://www.sparsity.ai/}\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \
%\faGlobe \ \url{https://www.amascolo.github.io}\ \ \ \ \ \ \ \ \ \ \ \ \ \
\faPhone \ \href{tel:+44-74533-31777}{+44 74 5333 1777}\ \
\faEnvelope \ \href{mailto:alexander.mascolo@gmail.com}{\nolinkurl{alexander.mascolo@gmail.com}}
}}

\begin{resume}

\section{PROFILE} Strong coding and analytical skills $\cdot$ 8+ years experience  at startups and trading desks.

\section{CURRENT}

{\sl MSc (by Research) Computer Science}
\hfill 2024 -- 2025\\
\textbf{University of Edinburgh} \hfill \textsc{edinburgh} \uk
\vspace{4pt}
\begin{itemize}
	\item Fully funded, systems research on compilers for data science.
	\item Open-sourced a query engine with code generation (\faGithub\  \href{https://github.com/edin-dal/sdql}{\texttt{sdql}}).
\end{itemize}

\section{EXPERIENCE}

{\sl Research Engineer}\hfill 2021 -- 2023\\
\textbf{Tably} \hfill \textsc{london} \uk
\vspace{4pt}
	\begin{itemize}
		\item Applied R\&D for large-scale distributed stream processing.
		\item Implemented conflict-free replicated data types (\faGithub\  \href{https://github.com/tablyinc/otto-test}{\texttt{otto}}).
	\end{itemize}

{\sl Software Engineer}\hfill 2019 -- 2020\\
\textbf{Gyana} \hfill \textsc{london} \uk
\vspace{4pt}
	\begin{itemize}
		\item Greenfield development of high-performance analytics libraries.
		\item Funding by top VC investors, including the founder of Twitter.
	\end{itemize}

{\sl Quantitative Developer} \hfill 2017 -- 2019\\
\textbf{Macquarie Group} \hfill \textsc{london} \uk
\vspace{4pt}
	\begin{itemize}
		\item Strategist role in Quantitative Investment Strategies (QIS).
		\item Coded up strategies and improved the backtesting engine.
	\end{itemize}

{\sl Quantitative Developer} \hfill 2015 -- 2016\\
\textbf{Macquarie Group} \hfill \textsc{sydney} \au
\vspace{4pt}
	\begin{itemize}
		\item Desk analytics role aligned with Options Market Making.
		\item Built visualisation tools to monitor trade execution latency.
	\end{itemize}

\section{EDUCATION}

{\sl BSc (Hons I) Computer Science}
	\hfill 2011 -- 2015\\
\textbf{Australian National University} \hfill \textsc{canberra} \au
\vspace{4pt}
	\begin{itemize}
		\item Interdisciplinary thesis on computer science and economic theory.
		\item National Merit Scholar (top 0.35\%), joint prize with mathematics.
		\item Teaching assistant for Logic, Formal Methods, Information Theory.
	\end{itemize}

{\sl Summer School in Logic and Formal Epistemology} \hfill 2013\\
\textbf{Carnegie Mellon University} \hfill \textsc{pittsburgh} \us
\vspace{4pt}
	\begin{itemize}
		\item Fully funded, seminars on statistical machine learning.
	\end{itemize}

%\section{PAPERS}
%
%\bibentry{sdql}

\section{CODING}

{\sf Python} $\CIRCLE \CIRCLE \CIRCLE \CIRCLE \LEFTcircle$ $\cdot$ {\sf Rust} $\CIRCLE \CIRCLE \CIRCLE \Circle \Circle$ $\cdot$ {\sf Scala} $\CIRCLE \CIRCLE \Circle \Circle \Circle$ $\cdot$ {\sf \Cpp} $\CIRCLE \Circle \Circle \Circle \Circle$

\section{CITIZENSHIP}

\au \ \textsf{Australian} \uk \ \textsf{British} \ita \ \textsf{Italian} (triple) $\cdot$ eligible for \us \ \textsf{US E-3} visa (\textsf{H-1B} not required).

\end{resume}
\end{document}